Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-02 paper/main.tex
shuffle up sections explaination

As proposed by Butler et al \cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}, data can be represented as a map from the base space \dbase\ to the fiber space \dfiber. This map is called a section $\dsection: \dbase \rightarrow \dtotal$ of the fiber bundle

@@

and the set of all sections over \dbase\ is denoted $\Gamma(\dbase, \dtotal)$. Sections can also be defined locally, meaning over an open set $\openset \subseteq \dtotal$, and the set of all sections over an arbitrary open set is

\begin{equation}
  \label{eq:related-work:continuity:sections}
  \begin{split}
  \cgamma{\opensetc}{\dtotalc|_{\opensetc}} \coloneqq \{&\dsectionc^{0}, \cdots, \dsectionc^{i}, \cdots, \dsectionc^{n}\} \\
   &\dsectionc: \opensetc\rightarrow \dtotalc|_{\openset}
  \end{split}
\end{equation}
 is the set of all data sets with a shared fiber \dfiber\ and continuity \dbase. The set of all sections defined over the total base space is denoted $\Gamma(\dbase, \dtotal)$.

@@

\begin{definition} \label{def:category:K} The category of open sets $\mathcal{\dbasec}$ consists of
  \begin{itemize}
    \item \textit{objects} open sets $\openset_{i} \in \{openset\}$ in the topological space $(\dbase, \mathscr{T})$), including the empty set $\varnothing$ and the maximum set \dbase. 
    \item \textit{morphisms} $\iota: \openset_{i} \hookrightarrow \openset_{j}$ for all  $\openset_i, \openset_j \subset \dtotal$
  \end{itemize} 
\end{definition}

We model data as the sheaf  $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op} \textcolor{sheaf}{\rightarrow} \setc$.
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc}{\dtotalc|_{\opensetc}} \in Ob(\setc) & \\
    {} & & {} \\
    & \opensetc \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)"', shift left = 10, color=sheaf] &   
\end{tikzcd}
\end{equation}
The objects of \textbf{Set} in this sheaf are the sets of sections $\Gamma(\dbase, \dtotal)$ introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps $(\iota, \iota^*)$ introduced in \autoref{eq:related-work:continuity:presheaf}.

The continuity of the graphic is encapsulated as a category $\mathcal{\mathcal{\gbase}}$ containing open set objects $\opensetg$, the complete set of opensets $\gbase$ that is the full space of the graphic, and the empty set. As with $\mathcal{\dbase}$, the morphisms between the open sets  $\opensetg$ are inclusion morphisms $\iota$. Over the graphic space $\opensetg \subseteq \gbase$ are a set of sections 
\begin{equation}
  \label{eq:artist:graphic_sections}
    \begin{split}
    \cgamma{\opensetgc}{\gtotalc|_{\opensetgc}} \coloneqq \{&\gsectionc^{0}, \cdots, \gsectionc^{i}, \cdots, \gsectionc^{n}\} \\
     &\gsectionc: \opensetgc\rightarrow \gtotalc|_{\opensetgc}
    \end{split}
  \end{equation}
\end{equation}
which are the set of all graphics with a shared base space and fiber and are a subcategory of \textbf{Set}. This allows us to represent the full space of graphics as a sheaf $\sheaf(\gtotal)$
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}[row sep=huge]
    {\cgamma{\opensetgc}{\gtotalc|_{\opensetgc}}}&  & 
    \textcolor{set}{\{}\gsectionc:\opensetgc\rightarrow \gtotalc\textcolor{set}{\}}
    \arrow[ll, "\iota"', hook', color=set] \\ &  & \\
    \opensetgc \arrow[uu, "\sheafc(\gtotalc)", color=sheaf] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheafc_{\vartistc}(\gtotalc)" description, dashed, color=sheaf] &  & 
    \end{tikzcd}
\end{equation}
The set of graphics reachable through an artist function is a subset of sections of the full set of graphics $\{\gsection\} \subset \Gamma(\opensetg, \gtotal|_{\opensetg})$. These sets of reachable graphics over open sets \opensetg\ are also objects of \textbf{Set}. This allows us to formulate the graphic output by the artist as a sheaf $\sheaf_{\vartist}$ from the graphic base space to the set of reachable graphics.

@@

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindex^*$ is a map from a repetition of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindex^*$ between a total space over graphics $\vindex^*\dtotal$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindex^*$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
 \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\xrightarrow{\vindex^*}} \cgamma{\gbasec}{\vindexc^*\dtotalc}
\end{equation}
to generate a set of equivalent sections over the graphic $\Gamma(\gtotal, \vindex^*{\dtotal})$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf_gamma}
\sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \cgamma{\gbasec}{\vindexc^*{\dtotalc}}
\end{equation}
which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\vindexc^*}: \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}

Following from \autoref{eq:artist:data_pullback_sheaf} and the construction of the artist sheaf in \autoref{eq:artist:artist_sheaf}, we propose that the artist function $\vartist$ is a natural transformation

\begin{equation}
  \label{eq:artist:natural-transform-diagram}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] & \\
\mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexc_*}(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &  & {\setc}\\
    & {} &                            
\end{tikzcd}
\end{equation}

>>>>

 There is a map from a point on the base space \dbase\ which returns values in the fiber space \dfiber. This map is called a section $\dsection: \dbase \rightarrow \dtotal$ of the fiber bundle

@@

and the set of all sections over \dbase\ is denoted $\Gamma(\dbase, \dtotal)$ . Sections can also be defined locally, meaning over an open set $\openset \subseteq \dtotal$ and the set of all sections over an arbitrary open set is $\Gamma(\openset, \dtotal)$. 
\begin{equation}
  \label{eq:related-work:continuity:sections}
  \begin{split}
  \cgamma{\opensetc}{\dtotalc|_{\opensetc}} \coloneqq \{&\dsectionc^{0}, \cdots, \dsectionc^{i}, \cdots, \dsectionc^{n}\} \\
   &\dsectionc: \opensetc\rightarrow \dtotalc|_{\openset}
  \end{split}
\end{equation}
Butler et al proposed that \cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992} sections could be used to model data sets since they are maps from a point on the continuity to a point in the fiber, and therefore they encapsulate both. The set of sections is the space of all data sets with the same continuity and fields.

@@

\begin{definition} \label{def:category:K} The category of open sets $\mathcal{\dbasec}$ consists of
  \begin{itemize}
    \item \textit{objects} open sets $\openset_{i} \in \{\openset\}$ in the topological space $(\dbase, \mathscr{T})$), including the empty set $\varnothing$ and the maximum set \dbase. 
    \item \textit{morphisms} $\iota: \openset_{i} \hookrightarrow \openset_{j}$ for all  $\openset_i, \openset_j \subset \dtotal$
  \end{itemize} 
\end{definition}

We model a space of data sets with the same continuity and fields as the sheaf  $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op} \textcolor{sheaf}{\rightarrow} \setc$.
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc}{\dtotalc|_{\opensetc}} \in Ob(\setc) & \\
    {} & & {} \\
    & \opensetc \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)"', shift left = 10, color=sheaf] &   
\end{tikzcd}
\end{equation}
The objects of \textbf{Set} in this sheaf are the sets of sections $\Gamma(\dbase, \dtotal)$ introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps $(\iota, \iota^*)$ introduced in \autoref{eq:related-work:continuity:presheaf}. As mentioned in \autoref{re} sections $\dsection$ are

\note{add transition sentence about artist }

The continuity of the graphic is encapsulated as a category $\mathcal{\gbase}}$

\begin{definition} The category of open sets $\mathcal{\gbase}$ in the topological space $(\dbase, \mathscr{T})$). This category consists of open set \textit{objects} $\opensetg \in \{\opensetg\}$, including the empty set \varnothing\ and the total set $\gtotal$, and inclusion \textmorphisms $\iota: \opensetg_i \rightarrow \opensetg_j$.  
\end{definition}

@@

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindex^*$ is a map from a repetition of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindex^*$ between a total space over graphics $\vindex^*\dtotal$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindex^*$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
 \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\xrightarrow{\vindex^*}} \cgamma{\gbasec}{\vindexc^*\dtotalc}
\end{equation}
to generate a set of equivalent sections over the graphic $\Gamma(\gtotal, \vindex^*{\dtotal})$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf_gamma}
\sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \cgamma{\gbasec}{\vindexc^*{\dtotalc}}
\end{equation}
which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}

As with $\mathcal{\dbase}$, the morphisms between the open sets  $\opensetg$ are inclusion morphisms $\iota$. Over the graphic space $\opensetg \subseteq \gbase$ are a set of sections 
\begin{equation}
  \label{eq:artist:graphic_sections}
    \begin{split}
    \cgamma{\opensetgc}{\gtotalc|_{\opensetgc}} \coloneqq \{&\gsectionc^{0}, \cdots, \gsectionc^{i}, \cdots, \gsectionc^{n}\} \\
     &\gsectionc: \opensetgc\rightarrow \gtotalc|_{\opensetgc}
    \end{split}
  \end{equation}
\end{equation}
which are the set of all graphics with a shared base space and fiber and are a subcategory of \textbf{Set}. This allows us to represent the full space of graphics as a sheaf $\sheaf(\gtotal)$
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}[row sep=huge]
    {\cgamma{\opensetgc}{\gtotalc|_{\opensetgc}}}&  & 
    \textcolor{set}{\{}\gsectionc:\opensetgc\rightarrow \gtotalc\textcolor{set}{\}}
    \arrow[ll, "\iota"', hook', color=set] \\ &  & \\
    \opensetgc \arrow[uu, "\sheafc(\gtotalc)", color=sheaf] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheafc_{\vartistc}(\gtotalc)" description, dashed, color=sheaf] &  & 
    \end{tikzcd}
\end{equation}
The set of graphics reachable through an artist function is a subset of sections of the full set of graphics $\{\gsection\} \subset \Gamma(\opensetg, \gtotal|_{\opensetg})$. These sets of reachable graphics over open sets \opensetg\ are also objects of \textbf{Set}. This allows us to formulate the graphic output by the artist as a sheaf 
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \sheafc_{\vartist}(\gtotalc): \gbasec^{\textcolor{base}{op}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}
from the graphic base space to the set of reachable graphics.

Following from \autoref{eq:artist:data_pullback_sheaf} and \autoref{eq:artist:artist_sheaf},  we propose that the artist function $\vartist$ is a natural transformation
\begin{equation}
  \label{eq:artist:natural-transform-diagram}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] & \\
\mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexc_*}(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &  & {\setc}\\
    & {} &                            
\end{tikzcd}
\end{equation}
